Executive Constraints and Civil Conflict Onset

### 2020-01-21 paper.Rmd
Add missing import and update path locations

[//]: # Setup R environment for entire doc
```{r include = F, results = "hide"}
knitr::opts_chunk$set(echo = F, eval = F)

library(dplyr)
library(thesis.utils)
```

@@

>>>>

[//]: # Setup R environment for entire doc
```{r include = F, results = "hide"}
knitr::opts_chunk$set(echo = F, eval = T)

library(dplyr)
library(extraDistr)
library(ggplot2)
library(gridExtra)
library(thesis.utils)
```

@@

In order

```{r}
prior_plot <- function(range, fn, title = NULL, ...) {
    data.frame(x = range) %>%
        ggplot(aes(x)) +
        stat_function(fun = fn, ...) +
        ggtitle(label = title) +
        theme(axis.title.y = element_blank(),
              axis.text.y = element_blank(),
              axis.ticks.y = element_blank())
}

p1 <- prior_plot(c(-20, 20), dnorm, args = list(mean = 0, sd = 5),
                 title = "Normal(0, 5)")
p2 <- prior_plot(c(-10, 10), dnorm, args = list(mean = 0, sd = 2.5),
                 title = "Normal(0, 2.5)")
p3 <- prior_plot(c(0, 5), dlnorm, args = list(meanlog = 0, sdlog = 0.5),
                 title = "Log-Normal(0, 0.5)")
p4 <- prior_plot(c(0, 3), dweibull, args = list(shape = 5, scale = 1),
                 title = "Weibull(5, 1)")
p5 <- prior_plot(c(0, 10), dhcauchy, args = list(sigma = 1),
                 title = "HalfCauchy(0, 1)")
p6 <- prior_plot(c(0, 1), dbeta, args = list(shape1 = 5, shape2 = 5),
                 title = "Beta(5, 5)")

grid.arrange(p1, p2, p3, p4, p5, p6, ncol = 2, nrow = 3)

```{r warning = F}
load("posteriors/sim/simulated_summary.RData")

ggplot(pars.df, aes(parameter, point, color = type)) +
    geom_point() +
    geom_errorbar(aes(parameter, ymin = codelow, ymax = codehigh),
                  width = 0) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

```{r warning = F}
latent.df <- arrange(latent.df, true_value) %>%
    mutate(idx = 1:n())

ggplot(latent.df, aes(idx, true_value)) +
    geom_point(col = "darkgrey") +
    geom_errorbar(aes(ymin = codelow, ymax = codehigh), alpha = 0.2, col = "darkblue") +
    ylab("True Value") +
    theme(axis.text.x = element_blank(),
          axis.title.x = element_blank(),
          axis.ticks.x = element_blank())
```

```{r results = 'hide'}
x <- with(latent.df, mean(true_value <= codehigh & true_value >= codelow))

#plot(df$lg_se[, 1], df$lg[, 1] - colMeans(lg_est))
#plot(df$lg_se[, 1], lapply(lg_est, IQR) %>% unlist)

#which(df$lg[, 1] + 2 * df$lg_se[, 1] < colMeans(lg_est) |
#      df$lg[, 1] - 2 * df$lg_se[, 1] > colMeans(lg_est))

#v <- lapply(theta_old, IQR) %>% unlist
#plot(df$lg_se[, 1], v[df$obs_idx])

#plot(density(p), xlim = c(0, 1), ylim = c(0, 2))
#for (i in 1:100) lines(density(p_hat[i, ]), col = alpha("lightblue", 0.2))

#table(colMeans(p_hat) > .5, y)

`r x * 100`
